---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "./man/figures/README-",
    fig.align = "center",
    collapse = TRUE,
    comment = "#>"
)
```

# connectcore

<!-- badges: start -->
<!-- badges: end -->

Shared transport base for R data-source connectors. Every connector we write тАФ
exchange REST/WebSocket APIs, AIS vessel feeds, any push or pull data source тАФ
was re-implementing the same plumbing: an httr2 request funnel, request signing,
JSON-to-`data.table` coercion, epoch-to-`POSIXct` conversion, and a reconnecting
WebSocket loop. `connectcore` is that plumbing, extracted once and shared.

It owns **transport only** тАФ it carries no trading vocabulary and does not depend
on `tradebot-core`. A connector package extends the two base classes and supplies
the venue specifics (the base URL, how to sign a request, how to read an error
envelope, how to turn a frame into events); everything else is inherited.

Two bases and a toolkit:

- **`RestClient`** тАФ an abstract REST client (sync **or** async via promises,
  optional retry and client-side throttle), with one `private$.request()` funnel
  every endpoint method delegates to. Venue specifics plug in by overriding two
  private seams: `.sign()` and `.parse_envelope()`.
- **`StreamClient`** тАФ an event-driven WebSocket base (`$on("message", ...)`,
  Node-style), with auto-reconnect (full-jitter backoff), keepalive, a silence
  watchdog, and proactive reconnect тАФ all handled for you. Subclasses override
  `.dispatch()` (frame тЖТ events) and `.resubscribe()` (replay subscriptions).
- **Helpers** тАФ request signing, JSONтЖТ`data.table` coercion, epochтЖФ`POSIXct`
  conversion, environment-backed credential loading, and WebSocket backoff. All
  typed and runtime-checked with [roxyassert](https://github.com/dereckscompany/roxyassert).

## Installation

This package uses [renv](https://rstudio.github.io/renv/); install it into the
project library:

```r
renv::install("dereckscompany/connectcore")
```

## Transport helpers

The coercion toolkit turns parsed JSON (lists) into flat `data.table`s with
snake_case columns and no list columns:

```{r}
library(connectcore)

# A JSON array of objects -> one data.table, names snake_cased, missing filled.
records <- list(
    list(openTime = 1700000000000, closePrice = "100.5", symbol = "BTCUSDT"),
    list(openTime = 1700000060000, closePrice = "101.0")
)
as_dt_list(records)
```

Epoch values (APIs deliver milliseconds, nanoseconds, or seconds) convert to
`POSIXct` in UTC and back:

```{r}
epoch_to_datetime(1700000000000, "ms")
datetime_to_epoch(epoch_to_datetime(1700000000000, "ms"), "s")
```

## Request signing

`hmac_query_sign()` implements the Binance-style scheme (HMAC-SHA256 of the
URL-encoded query string, plus an API-key header). The parameter and header
names are configurable, so one implementation serves any exchange that uses it.
Passing a fixed clock makes the signature reproducible:

```{r}
req <- httr2::req_url_query(httr2::request("https://api.example.com/order"), symbol = "BTCUSDT")
signed <- hmac_query_sign(
    req,
    keys = list(api_key = "PUBLIC", api_secret = "SECRET"),
    get_timestamp_ms = function() 1700000000000
)
httr2::url_parse(signed$url)$query
```

## Extending the REST base

A connector subclasses `RestClient` and overrides the two private seams. The
default `.sign()` applies no auth (a public client) and the default
`.parse_envelope()` is "JSON body, error on non-2xx" тАФ so a simple public API
needs no overrides at all.

```{r}
BinanceBase <- R6::R6Class(
    "BinanceBase",
    inherit = connectcore::RestClient,
    public = list(
        initialize = function(keys = NULL, base_url = "https://api.binance.com") {
            super$initialize(keys = keys, base_url = base_url, body_format = "query")
        }
    ),
    private = list(
        # Authenticate by delegating to the shared HMAC-query helper.
        .sign = function(req, keys, ctx) {
            connectcore::hmac_query_sign(req, keys, ctx$get_timestamp_ms)
        }
    )
)

client <- BinanceBase$new()
client$is_async
```

Set `async = TRUE` and every endpoint method returns a `promises::promise`
instead of a value тАФ the class is mode-transparent, the only branch is inside
`then_or_now()`.

## Extending the WebSocket base

`StreamClient` is event-driven, like `ws.on(...)` in Node. The base emits a
standard core of events (`open`, `message`, `close`, `error`, `reconnecting`,
`reconnected`, `giveup`, `stale` тАФ see `WS_EVENTS`); a subclass' `.dispatch()`
may emit its own. A minimal recorder needs no subclass тАФ register a handler and
run the loop:

```r
ws <- StreamClient$new("wss://stream.example.com", stale_timeout = 120)
ws$on("open", function(e) ws$send('{"subscribe": "all"}'))
ws$on("message", function(msg) cat(msg, "\n"))
ws$run() # keeps the process alive and pumps the event loop
```

The reconnect backoff is full-jitter exponential, capped, so a reconnect storm
can never trip a server's connection rate limit:

```{r}
vapply(1:5, function(attempt) ws_backoff_delay(attempt, cap_seconds = 60), numeric(1))
```

## Build commands

```bash
./scripts/BUILD.sh all       # document -> clean -> build -> check -> install
./scripts/BUILD.sh document  # regenerate documentation (and roxyassert contracts)
./scripts/BUILD.sh readme    # render README.Rmd -> README.md
./scripts/FORMAT.sh          # format R code with air
./scripts/LINT.sh            # lintr over the package
```

## License

MIT
