---
title: "Extending connectcore"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extending connectcore}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(connectcore)
```

`connectcore` is a base to extend, not an end-user package. It carries the
transport plumbing a data-source connector repeats — an httr2 request funnel,
request signing, JSON→`data.table` coercion, and a reconnecting WebSocket loop —
so a connector supplies only what is genuinely source-specific and inherits the
rest. Transport only: no domain vocabulary, no domain dependencies.

Two things are usable directly — the exported helpers, and `StreamClient` (it is
concrete; a recorder needs no subclass). The REST side is extend-only:
`RestClient`'s request funnel is private, reached by subclassing.

## The helpers, standalone

The coercion and time helpers are plain functions — call them anywhere:

```{r}
records <- list(
  list(openTime = 1700000000000, closePrice = "100.5", symbol = "ABC"),
  list(openTime = 1700000060000, closePrice = "101.0")
)
as_dt_list(records)

epoch_to_datetime(1700000000000, "ms")
```

## Extending the REST base

Subclass `RestClient` and override the two private seams. `.sign()` authenticates
a request (the default is no-auth); `.parse_envelope()` turns a response into data
and raises on error (the default is "JSON body, error on non-2xx"). Endpoint
methods delegate to the private `.request()` funnel, which injects the base URL,
credentials, both seams, and the retry/throttle config.

```{r}
MyClient <- R6::R6Class(
  "MyClient",
  inherit = connectcore::RestClient,
  public = list(
    initialize = function(keys = NULL, base_url = "https://api.example.com") {
      super$initialize(keys = keys, base_url = base_url, body_format = "query")
    },
    # A public endpoint method — the funnel is private, so this is how callers
    # reach it.
    ticker = function(symbol) {
      private$.request("/v1/ticker", query = list(symbol = symbol))
    }
  ),
  private = list(
    # Authenticate by delegating to the shared HMAC-query helper.
    .sign = function(req, keys, ctx) {
      connectcore::hmac_query_sign(req, keys, ctx$get_timestamp_ms)
    }
  )
)

client <- MyClient$new()
client$is_async
```

Constructing with `async = TRUE` makes every endpoint return a
`promises::promise` instead of a value — the class is mode-transparent, so the
method bodies above do not change.

## Extending the WebSocket base

`StreamClient` is event-driven, like `ws.on(...)` in Node. A minimal recorder
needs no subclass — register a handler and run the loop:

```{r, eval = FALSE}
ws <- StreamClient$new("wss://stream.example.com", stale_timeout = 120)
ws$on("open", function(e) ws$send('{"subscribe": "all"}'))
ws$on("message", function(msg) cat(msg, "\n"))
ws$run() # keeps the process alive and pumps the event loop
```

Subclass it only to classify frames into your own events (`.dispatch()`) or to
replay subscriptions after every (re)connect (`.resubscribe()`); the
reconnect / keepalive / watchdog machinery is inherited.

```{r, eval = FALSE}
MyStream <- R6::R6Class(
  "MyStream",
  inherit = connectcore::StreamClient,
  private = list(
    # Turn one raw frame into typed events instead of the default "message".
    .dispatch = function(raw) {
      msg <- jsonlite::fromJSON(raw, simplifyVector = FALSE)
      private$.emit(msg$type %||% "message", msg)
    },
    # Re-send subscriptions after each (re)connect.
    .resubscribe = function() {
      self$send('{"subscribe": "trades"}')
    }
  )
)
```

That is the whole contract: supply the source specifics, inherit the transport.
